Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/Error_Analysis.tex

In this section, we present our error analysis assuming that a fixed-point word lengths is given.
Then in the next section, we explain our optimization algorithm which determines suitable word
lengths fully automatically.
% in~\autoref{sec:Controller_Synthesis}.
While we do not employ the error analysis independently of the controller and
precision synthesis, we note that it is an alternative way of bounding errors to
existing methods~\cite{imperialrmpc}, which phrase the roundoff error computation as a (relaxed)
mixed integer programming problem.
%\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}

For simplicity of notation, we assume in this section a uniform word length $p$,
but our algorithm (and implementation) is applied to mixed-precision to reduce the memory usage.

@@

Due to the affinity of function
$v_{i}-v_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
to evaluate the function only at the corner points of the tube, and keep the
result with the maximal magnitude. 
To evaluate the incorrect region selection error across
the corner points, we need to first locate the corner points as well as all the
regions which share those corner points. 
Each region $R_i$ is represented by a set of contraints. We first extract the
set of vertices of $R_i$ using the open source Matlab library
$\mathit{lcon2vert}$~\cite{lcon2vertMatlab}.
For each computed vertex $v_i$, we compute a $n-D$
hypercube with the edge length of $2 \varepsilon$. 
Each of the $2^n$ vertices of this hypercube is counted as a corner point, on which
we evaluate $\|u_i - u_j\|$.

>>>>

In this section, we present our error analysis assuming that a fixed word length $p$ is given.
Then in the next section, we explain our optimization algorithm which determines suitable word
lengths for different variables fully automatically. % in~\autoref{sec:Controller_Synthesis}.
%
% For simplicity of notation, we assume in this section a uniform word length $p$,
% but our algorithm (and implementation) is applied to mixed-precision to reduce the memory usage.

@@

Since $v_{i}-v_{j}$ is also affine, and because we defined the tube as a convex region 
surrounding the corresponding hyperplane, it suffices
to evaluate the function only at the corner points of the tube, and keep the
result with the maximal magnitude. 
To evaluate the incorrect region selection error across
the corner points, we need to first locate the corner points as well as all the
regions which share those corner points. 
Each region $R_i$ is represented by a set of contraints. We first extract the
set of vertices of $R_i$ using the open source Matlab library
$\mathit{lcon2vert}$~\cite{lcon2vertMatlab}.
For each computed vertex $v_i$, we compute a $n$-dimensional
hypercube with the edge length of $2 \varepsilon$. 
Each of the $2^n$ vertices of this hypercube is counted as a corner point, on which
we evaluate $\|u_i - u_j\|$.
